Practical Machine Learning Course Project
========================================================
Aleksey Movchanyuk  
21 September 2014


## Abstract
We use the random forest method to estimate features for the Human Activity Recognition data set from Groupware. We that this method produces relevant results.


## Data
The data is taken from the [Human Activity Recognition](http://groupware.les.inf.puc-rio.br/har) programme at [Groupware](http://groupware.les.inf.puc-rio.br/).

We start the data loading procedure by specifying the data sources and destinations.

```{r echo=FALSE}
## including package
library(caret)
library(randomForest)
```

```{r}
## Read row data
trainingFile <- 'pml-training.csv'
testingFile     <- 'pml-testing.csv'

training <- read.csv(trainingFile, na.strings = c("", "NA", "#DIV/0!") )
testing <- read.csv(testingFile, na.strings = c("", "NA", "#DIV/0!") )

## Remove 1,5,6 columns 
training       <- training[,-c(1,5,6)]
testing        <- testing[,-c(1,5,6)]


## Define cross validation
## splitting the training data into a test set and a training set
library(caret)

trainingIndex  <- createDataPartition(training$classe, p=.60, list=FALSE)
training.train <- training[ trainingIndex,]
training.test  <- training[-trainingIndex,]
```

Remove entire NAs columns and removes any variables with missing NAs.
```{r}
## Remove entire NAs columns
rm.na.cols     <- function(x) { x[ , colSums( is.na(x) ) < nrow(x) ] }

training.train <- rm.na.cols(training.train)
training.test  <- rm.na.cols(training.test)


## Removes any variables with missing NAs
complete       <- function(x) {x[,sapply(x, function(y) !any(is.na(y)))] }

training.train <- complete(training.train)
training.test  <- complete(training.test)
```


## Method
We use the **Random Forests** method [@breiman2001random], which applies **bagging** to **tree learners**. 

```{r}
library(randomForest)
random.forest <- train(training.train[,-57],
                       training.train$classe,
                       tuneGrid=data.frame(mtry=3),
                       trControl=trainControl(method="none")
                       )
```


## Results
Some statistics on the results

```{r}
summary(random.forest)
```


We now compare the results from the predition with the actual data.

```{r}
confusionMatrix(predict(random.forest,
                        newdata=training.test[,-57]),
                training.test$classe
                )
```

```{r}
plot( varImp(random.forest) )
```

## References
